Generation of TypeScript Declaration Files from JavaScript Code

### 2021-05-20 mplr-2021/main.tex
streamlining section 4

As \texttt{dts-generate} is based on run-time information, code
fragments are needed that import and use the JavaScript library to
obtain run-time information from running the instrumented library
code.

The examples and the code base of the library are instrumented with
Jalangi \cite{DBLP:conf/sigsoft/SenKBG13} to gather data flow
information and type information at run time. Jalangi provides several
analysis modules that we extended as needed to retrieve the required
run-time information.
%, which is then saved in a JSON file.

A second independent block uses the run-time information to generate a
TypeScript declaration file. It infers the overall structure of the JavaScript
library, its interfaces, and the types from the run-time information. 
The resulting declaration file is ready for use in the development
process. Its contents mimic the usage of the library in the example
code fragments and match the structure of the
JavaScript library under analysis, so that the JavaScript code
generated after compiling the TypeScript code runs without
interface-related errors.

@@

To extract run-time information from a JavaScript library, it is
necessary, by definition, to execute the code, because the
analysis modules provided by Jalangi can only gather information if the instrumented code gets executed.

There are several options to obtain code fragments that drive the
library code:
\begin{enumerate}
\item\label{item:1} execute code that imports the library;
\item\label{item:2} execute the test cases that come with the library;
\item\label{item:3} execute code fragments extracted from the library documentation.
\end{enumerate}

Option~\ref{item:1} does not solve our problem, it just delegates it
to the importing library, which also needs code to drive it. Moreover,
we need to identify a dependent package, which is costly to download and instrument.

@@

% We can maybe change the focus to 'Option 3' was easier to implement.
% This can be another opportunity to mention that  
In the end, option~\ref{item:3} was the most viable option to easily gather runtime information
even though there is no standard for documentation, either. However, almost all repositories
contain README files where the library authors briefly describe in prose what
the code does, which problem it solves, how to install the
application, how to build the code, etc. It is very common that
developers provide code examples in the README files to show how the
library works and how to use it. These code fragments showcase common use cases rather
than stress-testing the implementation (the problem of
option~\ref{item:2}) because they are meant to be instructive to users of the package.

@@

\item Extract the code examples from the README file. To this end,
  observe that README files are
  written using Markdown\footnote{\url{https://www.markdownguide.org}}, a
  popular markup language, where
  code examples are presented in code blocks labeled with the programming
  language. Hence, we
  retrieve the code examples from code blocks labeled \texttt{js} or
  \texttt{javascript}, which both stand for JavaScript in
  Markdown.
\end{itemize}

@@

\begin{lstlisting}[
  caption={Extracted example code for the \texttt{glob-to-regexp} package},
  language=JavaScript,
  label=code:code-example-extracted-motivating-example,
  float,captionpos=b
]
var globToRegExp = require('glob-to-regexp');
var re = globToRegExp("p*uck");
re.test("pot luck"); // true
re.test("pluck"); // true
re.test("puck"); // true

@@

Obtaining the code fragments from the examples provided in the
README files of the repository proved to be an
appropriate and pragmatic way of extracting the developer's
intention and provides an initial code base with meaningful
examples.
%? , thus avoiding possible cold start problems.

@@

\begin{itemize}
  \item Function \lstinline{f} was invoked where parameter
    \lstinline{a} held a value of type \lstinline{string} and
    \lstinline{b} a value of type \lstinline{number}. 
  \item Property \lstinline{foo} of parameter \lstinline{a} of
    function \lstinline{f} was accessed within the function. 
  \item Parameter \lstinline{a} of function \lstinline{f} was used as
    operand for \lstinline{==}. 
\end{itemize}

The dynamic analysis framework Jalangi is used for gathering this kind of
information. Jalangi's configurable analysis modules enable
programming custom callbacks that can get triggered with virtually any
JavaScript event. Our instrumentation observes the following events: 
\begin{itemize}
  \item binary operations, like \lstinline{==}, \lstinline{+}, or
    \lstinline{===};
  \item variable declarations;
  \item function, method, or constructor invocations;
  \item access to an object's property;
  \item unary operations, like \lstinline{!} or \lstinline{typeof}.
\end{itemize}

The implementation stores these observations as entities called
\texttt{interactions}. They are used for translating, modifying, and
aggregating Jalangi's raw event information to get an application-specific data representation. Each function invocation is stored as
a \texttt{FunctionContainer} which contains an \texttt{ArgumentContainer} for each argument. Each \texttt{ArgumentContainer} contains 
the name and index of the argument and a collection of \texttt{interactions}. As shown in \figref{fig:example-get-field-interaction}, the interaction \texttt{getField} gets triggered whenever 
a property of an object gets accessed and it tracks the name of the accessed field and the type of the returned value. The invocation of an object's method is tracked with 
the \texttt{methodCall} interaction. The \texttt{followingInteractions} property is used for inferring nested interfaces.
It is an array that recursively records \texttt{interactions} on the return value of \texttt{getField} or 
\texttt{methodCall}. \figref{fig:example-method-call-interaction} provides an example for both the \texttt{methodCall} interaction
and the \texttt{followingInteractions} property. Finally, the \texttt{usedAsArgument} interaction
gets triggered when an argument is used in the invocation of a function.

\begin{figure*}[t]
  \centering
  \begin{subfigure}[t]{0.48\linewidth}
    \begin{lstlisting}[language=JavaScript,numbers=none]
function foo(hello) {
  if (hello.world) {
    // ...
  }
}

foo({ world: "..." });
    \end{lstlisting}
  \end{subfigure}
  \hfill
  \begin{subfigure}[t]{0.48\linewidth}
    \begin{lstlisting}[language=JavaScript,numbers=none,escapechar=!]
{
  functionId_1: {
    //...
    functionName: 'foo',
    args: {
      0: {
        //...
        argumentName: "hello",
        interactions: [
          // ...
          !\textbf{\{}!
            !\textbf{code: "getField",}!
            !\textbf{field: "world",}!
            !\textbf{followingInteractions: [],}!
            !\textbf{returnTypeOf: "string",}!
          !\textbf{\},}!
        ],
      },
    },
  },
}
    \end{lstlisting}
  \end{subfigure}
  \caption{
      Example code that for \texttt{getField} interaction
    }
  \label{fig:example-get-field-interaction}
\end{figure*}

\begin{figure*}[t]
  \begin{subfigure}[t]{0.48\linewidth}
      \begin{lstlisting}[language=JavaScript,numbers=none]
function foo(bar) {
  if (bar.hello().world) {
    // ...
  }
}

foo({
  hello: function () {
    return {
      world: "xxx",
    };
  },
});    
      \end{lstlisting}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.48\linewidth}
      \begin{lstlisting}[language=JavaScript,numbers=none,escapechar=!]
{
  functionId_1: {
    //...
    functionName: "foo",
    args: {
      0: {
        // ...
        argumentName: "bar",
        interactions: [
          // ...
          !\textbf{\{}!
            !\textbf{code: "methodCall",}!
            !\textbf{methodName: "hello",}!
            !\textbf{functionId: "functionId\_2",}!
            !\textbf{followingInteractions: [}!
              !\textbf{\{}!
                !\textbf{code: "getField",}!
                !\textbf{field: "world",}!
                !\textbf{followingInteractions: [],}!
                !\textbf{returnTypeOf: "string",}!
              !\textbf{\},}!
            !\textbf{],}!
          !\textbf{\},}!
        ],
      },
    },
  },
}        
      \end{lstlisting}
    \end{subfigure}
  \caption{Example code for \texttt{}{methodCall} and \texttt{followingInteractions}}
  \label{fig:example-method-call-interaction}
\end{figure*}

@@

We wrap each function's argument in a wrapper object, which  stores meta-information and greatly simplifies the mapping of an observation 
with the corresponding \texttt{ArgumentContainer} or \texttt{interaction}. We use the original values for critical operators such as 
\texttt{===} or \texttt{typeof}, for which wrapper objects would modify the behavior of the code.

The property \texttt{requiredModule} stores the name of the module that declared the invoked function. If a function is explicitly 
exported by the module, the property \texttt{isExported} will be set to \texttt{true} when it is invoked. If a function of an 
exported object is invoked, \texttt{isExported} will be \texttt{false} and \texttt{requiredModule} will contain the name of 
the required module, as shown in \figref{fig:example-is-exported-required-module}.

The run-time information is saved as a JSON file that can be used for later
processing. The instrumentation tool is written in JavaScript and runs in \NodeJS{} in a
Docker container.

@@

The next step in the pipeline after gathering the run-time information is
the generation of the declaration file (cf.\
\figref{fig:tsd_generation_method_block_diagram}). It is a lightweight,
simple, and fast application, which solely relies on the run-time
information gathered in the previous step.
% The tool itself is written in TypeScript and runs in a
% Docker container in \NodeJS.

Instead of analyzing the shape of the exported module, we choose the
template based on how the module is used. We analyze the properties \texttt{isExported},
\texttt{requiredModule}, and \texttt{isConstructor} from the
information gathered at run time to distinguish
between \textbf{module-class} and \textbf{module-function}. If a function is invoked and
it is imported from the module we are analyzing we infer the template
\textbf{module-class} or \textbf{module-function}. We choose \textbf{module-class} if the
function is used as a constructor. Otherwise, we choose
\textbf{module-function}.
If no function is invoked, we use the \textbf{module}
template.
% \figref{fig:dts-generate-choose-templates} exposes this logic using the example
% provided in \figref{fig:multi-purpose-module-example}.

@@

We implemented the most common TypeScript features first and we focused our effort in building an
end-to-end solution that generates useful declaration files. The
types \texttt{string}, \texttt{number}, \texttt{boolean}, unions
thereof, arrays, function callbacks, and optional elements were considered
both for function parameters and interface properties. We also
considered overloaded functions.
Common types such as
\texttt{any}, tuples, intersections (that
is, types formed using the intersection operator \lstinline[language=TypeScript]/&/) and features such as
generics and index signatures were not implemented.

The selection of typing features covered in the tool is driven by
examination of the files in
the DefinitelyTyped repository. We parsed each declaration file with
\texttt{dts-parse} and tagged it according to the features used in the file.
Table~\ref{tab:dts-parse-stats} summarizes the results.
We decided to prioritize the features with the highest number of
occurrences and support them first in our framework.

\begin{table}[tp]
  \caption{Distribution of TypeScript features in declaration files uploaded to DefinitelyTyped (DT). The 2nd column shows how many files in DT make use of a specific TypeScript feature. The 3rd column shows the corresponding percentage for a total of 6648 declaration files in DT. Numbers were obtained from commit \texttt{da93d7b13094bacb170ead3f4a289f3b8687e4e5} (April 4, 2020).}
  \begin{center}
    \begin{tabular}{ |l|c|r| } 
      \hline
      \textbf{TypeScript feature} & \textbf{Count} & \multicolumn{1}{|c|}{\textbf{\%}} \\ 
      \hline
      type-string & 5086 & 76.50\% \\
      optional-parameter & 4915 & 73.93\% \\
      type-boolean & 3891 & 58.53\% \\
      type-number & 3699 & 55.64\% \\
      type-void & 3548 & 53.37\% \\
      type-union & 3456 & 51.99\% \\
      type-function & 3286 & 49.43\% \\
      type-array & 3264 & 49.10\% \\
      type-any & 3127 & 47.04\% \\
      type-literals & 1925 & 28.96\% \\
      alias-type & 1899 & 28.56\% \\
      index-signature & 1271 & 19.12\% \\
      generics-function & 1145 & 17.22\% \\
      dot-dot-dot-token & 882 & 13.27\% \\
      call-signature & 817 & 12.29\% \\
      generics-interface & 718 & 10.80\% \\
      type-object & 661 & 9.94\% \\
      type-undefined & 577 & 8.68\% \\
      type-intersection & 431 & 6.48\% \\
      readonly & 373 & 5.61\% \\
      type-tuple & 355 & 5.34\% \\
      generics-class & 265 & 3.99\% \\
      static & 251 & 3.78\% \\
      private & 82 & 1.23\% \\
      public & 43 & 0.65\% \\
      protected & 19 & 0.29\% \\
      \hline
    \end{tabular}
  \end{center}
  \label{tab:dts-parse-stats}
\end{table}

>>>>

As \texttt{dts-generate} is based on run-time information, we need code
fragments that import and use the JavaScript library and we need to be
able to obtain this run-time information while running the code.
We explain in Section~\ref{sec:initial-code-base} how we obtain code
fragments. 
To obtain run-time information, we instrument
the code fragments and the entire code base of the library with
Jalangi \cite{DBLP:conf/sigsoft/SenKBG13}. We extend Jalangi's
analysis modules to gather data flow and type information as required
for our purposes and explained in Section~\ref{sec:run-time-information}.
% Jalangi provides several
% analysis modules that we extended as needed to retrieve the required
% run-time information.
%, which is then saved in a JSON file.

A second independent block explained in
Section~\ref{sec:typescr-decl-file} uses the run-time information to
generate a TypeScript declaration file. It infers the overall
structure of the JavaScript library, its interfaces, and the types
from the run-time information.  The resulting declaration file is
ready for use in the development process. Its contents mimic the usage
of the library in the example code fragments and match the structure
of the JavaScript library under analysis, so that the JavaScript code
generated after compiling the TypeScript code runs without
interface-related errors.

@@

% To extract run-time information from a JavaScript library, it is
% necessary, by definition, to execute the code, because the
% analysis modules provided by Jalangi can only gather information if the instrumented code gets executed.

There are several options to obtain code fragments that exercise the
library code in a meaningful way. In order to exercise library $A$,
one might
\begin{enumerate}
\item\label{item:1} execute code that imports library $A$;
\item\label{item:2} execute the test cases that come with library $A$;
\item\label{item:3} execute code fragments extracted from library $A$'s documentation.
\end{enumerate}

Option~\ref{item:1} requires finding a library $B$ that depends on
$A$. While this information is straightforward to obtain from \NPM, it
is potentially costly to download and instrument $B$ for use with
Jalangi. Moreover, this option delegates our problem
to library $B$, which also needs code to drive it.

@@

% We can maybe change the focus to 'Option 3' was easier to implement.
% This can be another opportunity to mention that  
In the end, option~\ref{item:3} was the most viable option to gather run-time information
even though there is no standard for documentation, either. However, almost all repositories
contain README files where the library authors briefly describe in prose what
the code does, which problem it solves, how to install the
application, how to build the code, etc. It is very common that
developers provide code examples in the README files to show how the
library works and how to use it. These code fragments showcase common use cases rather
than stress-testing the implementation (a problem of
option~\ref{item:2}) because they are meant to be instructive to users of the package.

@@

\item Extract the code examples from the README file. To this end,
  observe that README files are
  written using Markdown\footnote{\url{https://www.markdownguide.org}}, a
  popular markup language, where most
  code examples are presented in code blocks labeled with the programming
  language. Hence, we
  retrieve the code examples from code blocks labeled \texttt{js} or
  \texttt{javascript}, which both stand for JavaScript.
\end{itemize}

@@

\begin{lstlisting}[
  caption={Code extracted from the \texttt{glob-to-regexp} package},
  language=JavaScript,
  label=code:code-example-extracted-motivating-example,
  float,captionpos=b
]
var globToRegExp = require('glob-to-regexp');
var re = globToRegExp("p*uck");
re.test("pot luck"); // true
re.test("pluck"); // true
re.test("puck"); // true

@@

Obtaining the code fragments from the examples provided in the
README files of the repository proved to be an
appropriate and pragmatic way of extracting the developer's
intention. It provides an initial code base with meaningful
examples.
%? , thus avoiding possible cold start problems.

@@

\begin{itemize}
  \item Function \lstinline{f} was invoked where parameter
    \lstinline{a} held a value of type \lstinline{string} and
    \lstinline{b} a value of type \lstinline{number}. 
  \item Function \lstinline{foo} was invoked. Its parameter
    \lstinline{hello} was accessed as an object within the
    function. Its property \lstinline{world} was found to have a
    string value (see Figure~\ref{fig:example-get-field-interaction}).
  \item Function \lstinline{foo} was invoked. Its parameter
    \lstinline{bar} was accessed as an object. Its method
    \lstinline{hello} was invoked. The return value of this call was
    accessed as an object with property \lstinline{world}, which
    returned a string (see Figure~\ref{fig:example-method-call-interaction}).
  \item Parameter \lstinline{a} of function \lstinline{f} was used as
    operand for \lstinline{==}. 
\end{itemize}

Jalangi's configurable analysis modules enable
programming custom callbacks that can get triggered with virtually any
JavaScript event. Our instrumentation observes the following events: 
\begin{itemize}
  \item binary operations, like \lstinline{==}, \lstinline{+}, or
    \lstinline{===};
  \item variable declarations;
  \item function, method, or constructor invocations;
  \item access to an object's property;
  \item unary operations, like \lstinline{!} or \lstinline{typeof}.
\end{itemize}

The implementation stores these observations as entities called
\texttt{interactions}, which document each operation applied. They are used for translating, modifying, and
aggregating Jalangi's raw event information to get an application-specific data representation. Each function invocation is stored as
a \texttt{FunctionContainer} which contains an \texttt{ArgumentContainer} for each argument. Each \texttt{ArgumentContainer} contains 
the name and index of the argument and a collection of
\texttt{interactions} on the argument. As shown in \figref{fig:example-get-field-interaction}, the interaction \texttt{getField} gets triggered whenever 
a property of an object gets accessed. It tracks the name of the
accessed field and the type of the returned value. The invocation of a
method is tracked with the \texttt{methodCall} interaction. An
interaction can have a \texttt{followingInteractions} property if
there are further operations on the return value of the interaction. It is used for inferring nested interfaces.
That is, the \texttt{followingInteractions} recursively record \texttt{interactions} on the return value of \texttt{getField} or 
\texttt{methodCall}, taking care of object identities to avoid
looping. \figref{fig:example-method-call-interaction} provides an
example for both the \texttt{methodCall} interaction 
and the \texttt{followingInteractions} property. There is a
\texttt{usedAsArgument} interaction (not shown) that
gets triggered when an argument is used in the invocation of another function.

\begin{figure}[t]
  \centering
    \begin{lstlisting}[language=JavaScript,numbers=none]
function foo(hello) {
  if (hello.world) {
    // ...
} }

foo({ world: "..." });
    \end{lstlisting}
    \begin{lstlisting}[language=JavaScript,numbers=none,escapechar=!]
{ functionId_1: {
    //...
    functionName: 'foo',
    args: {
      0: {
        //...
        argumentName: "hello",
        interactions: [
          // ...
          !\textbf{\{}!
            !\textbf{code: "getField",}!
            !\textbf{field: "world",}!
            !\textbf{followingInteractions: [],}!
            !\textbf{returnTypeOf: "string",}!
          !\textbf{\},}!],},},},}
    \end{lstlisting}
  \caption{
      Example code for \texttt{getField} interaction
    }
  \label{fig:example-get-field-interaction}
\end{figure}

\begin{figure}[t]
      \begin{lstlisting}[language=JavaScript,numbers=none]
function foo(bar) {
  if (bar.hello().world) {
    // ...
  }
}

foo({
  hello: function () {
    return {
      world: "xxx",
};},});    
      \end{lstlisting}

      \begin{lstlisting}[language=JavaScript,numbers=none,escapechar=!]
{ functionId_1: {
    //...
    functionName: "foo",
    args: {
      0: {
        // ...
        argumentName: "bar",
        interactions: [
          // ...
          !\textbf{\{}!
            !\textbf{code: "methodCall",}!
            !\textbf{methodName: "hello",}!
            !\textbf{functionId: "functionId\_2",}!
            !\textbf{followingInteractions: [}!
              !\textbf{\{}!
                !\textbf{code: "getField",}!
                !\textbf{field: "world",}!
                !\textbf{followingInteractions: [],}!
                !\textbf{returnTypeOf: "string",}!
              !\textbf{\},}! !\textbf{],}! !\textbf{\},}!],},},},}
      \end{lstlisting}
  \caption{\texttt{}{methodCall} and \texttt{followingInteractions}}
  \label{fig:example-method-call-interaction}
\end{figure}

@@

To obtain this information we wrap each function's argument in a wrapper object, which stores meta-information and provides the mapping of an observation 
to the corresponding \texttt{ArgumentContainer} or
\texttt{interaction}. For operators that are aware of object identity, such as 
\texttt{===} or \texttt{typeof}, we use the original values because
they could return different results for wrapper objects.

We also gather information to determine which  module template is most
appropriate. To this end
the property \texttt{requiredModule} stores the name of the module that declared the invoked function. If a function is explicitly 
exported by the module, the property \texttt{isExported} is set to \texttt{true} when it is invoked. If a function of an 
exported object is invoked, \texttt{isExported} will be \texttt{false} and \texttt{requiredModule} will contain the name of 
the required module, as shown in
\figref{fig:example-is-exported-required-module}. If a function is
used as a constructor, we set its \texttt{isConstructor} flag.

% The run-time information is saved as a JSON file that can be used for later
% processing. The instrumentation tool is written in JavaScript and runs in \NodeJS{} in a
% Docker container.

@@

The next step after gathering the run-time information is
the generation of the declaration file (cf.\
\figref{fig:tsd_generation_method_block_diagram}).
% It is a lightweight,
% simple, and fast application, which solely relies on the run-time
% information gathered in the previous step.
% The tool itself is written in TypeScript and runs in a
% Docker container in \NodeJS.  
%
Contrary to \texttt{dts-gen} which analyzes the shape of the exported module, we choose the
template based on the way the module is used. We analyze the properties \texttt{isExported},
\texttt{requiredModule}, and \texttt{isConstructor} from the
run-time information to distinguish
between \textbf{module-class} and \textbf{module-function}. If a function is invoked and
it is imported from the module we are analyzing we infer the template
\textbf{module-class} or \textbf{module-function}. We choose \textbf{module-class} if the
function is used as a constructor. Otherwise, we choose
\textbf{module-function}.
If no function is invoked, we use the \textbf{module}
template.
% \figref{fig:dts-generate-choose-templates} exposes this logic using the example
% provided in \figref{fig:multi-purpose-module-example}.

@@

Our goal is to support the  most commonly used TypeScript
features first in our implementation. To this end,
the selection of typing features covered in the tool is driven by
an analysis of the 6648 declaration files in
the DefinitelyTyped repository. \footnote{As of commit
  \texttt{da93d7b13094bacb170ead3f4a289f3b8687e4e5} (April 4, 2020).}
We parsed each declaration file with 
\texttt{dts-parse} and tagged it according to the features used in the file.
Table~\ref{tab:dts-parse-stats} summarizes the results.
The \textbf{Count} column indicates the number of declaration files that use a
specific feature. The 3rd column shows the corresponding
percentage with respect to all files in the repository.

We start with a limited scope on the features with the highest number of
occurrences. Thus, we focus our effort on building an
end-to-end solution that generates useful declaration files. We choose
the types \texttt{string}, \texttt{number}, \texttt{boolean}, unions
thereof, arrays, function callbacks, and optional elements are considered
both for function parameters and interface properties. We also
treat aliases and overloaded functions.
Some common types such as \texttt{any}, literals, generics, and index
signatures are not yet implemented. 
Rare types such as tuples and intersections (that
is, types formed using the intersection operator
\lstinline[language=TypeScript]/&/) were not considered.

\begin{table}[tp]
  \begin{center}
    \begin{tabular}{ |l|c|r| } 
      \hline
      \textbf{Feature} & \textbf{Count} & \multicolumn{1}{|c|}{\textbf{\%}} \\ 
      \hline
      type-string & 5086 & 76.50\% \\
      optional-parameter & 4915 & 73.93\% \\
      type-boolean & 3891 & 58.53\% \\
      type-number & 3699 & 55.64\% \\
      type-void & 3548 & 53.37\% \\
      type-union & 3456 & 51.99\% \\
      type-function & 3286 & 49.43\% \\
      type-array & 3264 & 49.10\% \\
      type-any & 3127 & 47.04\% \\
      type-literals & 1925 & 28.96\% \\
      alias-type & 1899 & 28.56\% \\
      index-signature & 1271 & 19.12\% \\
      generics-function & 1145 & 17.22\% \\
      dot-dot-dot-token & 882 & 13.27\% \\
      call-signature & 817 & 12.29\% \\
      generics-interface & 718 & 10.80\% \\
      type-object & 661 & 9.94\% \\
      type-undefined & 577 & 8.68\% \\
      type-intersection & 431 & 6.48\% \\
      readonly & 373 & 5.61\% \\
      type-tuple & 355 & 5.34\% \\
      generics-class & 265 & 3.99\% \\
      static & 251 & 3.78\% \\
      private & 82 & 1.23\% \\
      public & 43 & 0.65\% \\
      protected & 19 & 0.29\% \\
      \hline
    \end{tabular}
  \end{center}
  \caption{Usage of TypeScript features on DefinitelyTyped}
  \label{tab:dts-parse-stats}
\end{table}
